R Notebook

### 2022-05-30 code.Rmd
update code

```{r}
library(tidyverse)
house <- read.csv("/Users/atticusw/Desktop/pton-market-data.csv")

@@

house <- na.omit(house)
```

```{r}
#normalize numerical data

@@

performance <- function(df, modelName) {
  pf <- data.frame(modelName(df, 0))
  for (i in 1:9) {
    pf <- cbind(pf, modelName(df, i))
  }
  pf <- t(pf)
  print(c(mean(pf[,1]), mean(pf[,2])))
  return(c(mean(pf[,1]), mean(pf[,2])))
}
```

```{r}
#now we define the regression models!

@@

#performance(dummySplitWithResponse, PCRModel)
#This one has a higher R squared, but as a trade-off it also has higher variance
```

```{r}
#compare the models

>>>>

```{r}
library(tidyverse)
house <- read.csv("./data/pton-market-data.csv")

@@

house <- na.omit(house)

#normalize numerical data

@@

performance <- function(df, modelName) {
  pf <- data.frame(modelName(df, 0))
  for (i in 1:9) {
    pf <- cbind(pf, modelName(df, i))
  }
  pf <- t(pf)
  print(c(mean(pf[,1]), mean(pf[,2])))
  return(c(mean(pf[,1]), mean(pf[,2])))
}

#now we define the regression models!

@@

#performance(dummySplitWithResponse, PCRModel)
#This one has a higher R squared, but as a trade-off it also has higher variance

#compare the models
